---
title: "xbrlus"
output: 
  html_document: 
    keep_md: yes
---

This package provides an R interface to 
[XBRL US API](https://github.com/xbrlus/data_analysis_toolkit).


## Installation

```{r eval=FALSE}
devtools::install_github("bergant/xbrlus")
```

## Setup
All APIs (except for the `CIKLookup`) require use of a valid XBRL US API
key. You can get the key and read the terms of usage at
http://xbrl.us/use/howto/data-analysis-toolkit/.

__xbrlus__ package will read the API key from environment variable
`XBRLUS_API_KEY`.
To start R session with the initialized environment variable
create a file in your R home with a line like this:

`XBRLUS_API_KEY=EnterKeyHere`

and name it as `.Renviron`. To check where your R home is, type `normalizePath("~")` in your R console.

## Usage
Get information about companies and XBRL concepts with `xbrlCIKLookup` 
and `xbrlBaseElement`: 
```{r cache=TRUE}
library(xbrlus)

companies <- xbrlCIKLookup(c(
  "aapl", 
  "goog", 
  "fb"
)) 

elements <- xbrlBaseElement(c(
  "AssetsCurrent",
  "AssetsNoncurrent",
  "Assets",
  "LiabilitiesCurrent",
  "LiabilitiesNoncurrent",
  "Liabilities",
  "StockholdersEquity",
  "MinorityInterest",
  "StockholdersEquityIncludingPortionAttributableToNoncontrollingInterest",
  "LiabilitiesAndStockholdersEquity"
))
```

Use `xbrlValues` to get balance sheet values:
```{r cache=TRUE}
values <- xbrlValues(
  CIK = companies$cik, 
  Element = elements$elementName, 
  DimReqd = FALSE, 
  Period = "Y",
  Year = 2013,
  NoYears = 1,
  Ultimus = TRUE,
  Small = TRUE,
  as_data_frame = TRUE
)
```

Reshape to wide format and print table:
```{r message=FALSE}
library(dplyr)
library(tidyr)
library(htmlTable)

balance_sheet <- 
  elements %>% 
  left_join(values, by = "elementName") %>% 
  select(entity, standard.text, amount) %>% 
  mutate(amount = round(amount / 10e6,0)) %>%  
  spread(entity, amount )

balance_sheet <- balance_sheet[order(order(elements$elementName)), ]  
htmlTable(balance_sheet, 
          align="lrrr", align.header = "lrrr", 
          rnames = FALSE, 
          caption = "Bilance Sheet Comparison")
```


## References
Data Analysis Toolkit and API description on GitHub: https://github.com/xbrlus/data_analysis_toolkit
