---
title: "xbrlus"
output: 
  html_document: 
    keep_md: yes
---

This package provides an R interface to 
[XBRL US API](https://github.com/xbrlus/data_analysis_toolkit).



## Installation

```{r eval=FALSE}
devtools::install_github("bergant/xbrlus")
```

## Setup
All APIs (except for the `CIKLookup`) require use of a valid XBRL US API
key. You can get the key and read the terms of usage at
http://xbrl.us/use/howto/data-analysis-toolkit/.

__xbrlus__ package will read the API key from environment variable
`XBRLUS_API_KEY`.
To start R session with the initialized environment variable
create a file in your R home with a line like this:

`XBRLUS_API_KEY=EnterKeyHere`

and name it as `.Renviron`. To check where your R home is, type `normalizePath("~")` in your R console.

## Usage
Get information about companies and XBRL concepts with `xbrlCIKLookup` 
and `xbrlBaseElement`: 
```{r cache=TRUE}
library(xbrlus) 

companies <- xbrlCIKLookup(c(
  "aapl", 
  "goog", 
  "fb"
)) 

elements <- xbrlBaseElement(c(
  "AssetsCurrent",
  "AssetsNoncurrent",
  "Assets",
  "LiabilitiesCurrent",
  "LiabilitiesNoncurrent",
  "Liabilities",
  "StockholdersEquity",
  "MinorityInterest",
  "StockholdersEquityIncludingPortionAttributableToNoncontrollingInterest",
  "LiabilitiesAndStockholdersEquity"
))
```

Use `xbrlValues` to get balance sheet values:
```{r cache=TRUE}
values <- xbrlValues( 
  CIK = companies$cik, 
  Element = elements$elementName, 
  DimReqd = FALSE, 
  Period = "Y",
  Year = 2013,
  NoYears = 1,
  Ultimus = TRUE,
  Small = TRUE,
  as_data_frame = TRUE
)
```

Reshape to wide format and print table:
```{r message=FALSE, results='asis'}
library(dplyr)
library(tidyr)

balance_sheet <- 
  elements %>% 
  left_join(values, by = "elementName") %>% 
  select(entity, standard.text, amount) %>% 
  mutate(amount = round(amount / 10e6,0)) %>%  
  spread(entity, amount)

balance_sheet <- balance_sheet[
    order(order(elements$elementName)),   
    !is.na(names(balance_sheet))]
row.names(balance_sheet) <- NULL

library(pander)
pandoc.table(
  balance_sheet,
  caption = "Balance Sheet Comparison",
  big.mark = ",",
  split.table = 200,
  style = "rmarkdown",
  justify = c("left", rep("right", 3)))

```


## References
Data Analysis Toolkit and API description on GitHub: https://github.com/xbrlus/data_analysis_toolkit
